\addcontentsline{toc}{chapter}{Tài liệu tham khảo}
\begin{thebibliography}{9}

\bibitem{fraysse1} Fraysse, P. (2014). {\em Recursive Estimation in a Class of Models of Deformation, Journal of Statistical Planning and Inference}, 132-158.
	
\bibitem{bercu} Bercu, B. and Fraysse, P. (2012). {\em A Robbins-Monro Procedure for Estimation in Semiparametric Regression Models}.

\bibitem{duflo} Duflo, M. (1997). {\em Random Iterative Models. Applications of Mathematics(New York)}, Springer, Berlin.

\bibitem{bercuslide} Bercu, B. (2014). {\em Asymptotic Results for Martingales with Statistical applications}.

\bibitem{kushner} Kushner, H.J and Yin, G.G (2003). {\em Stochastic Approximation and Recursive Algorithms and Applications}. Applications of Mathematics(New York), Springer.

\bibitem{bruce} Bruce M. Brown (1971). {\em Martingale Central Limit Theorems}.

\bibitem{chaabane} Chaabane, F. and Maaouia, F. (2000). {\em Théorèmes Limites Avec Poids Pour Les Martingales Vectorielles}, ESAIM PS, 4, 137–189.

\bibitem{tien} Tiến, N.D. (2001). {\em Các mô hình xác suất và ứng dụng. Phần III, giải tích ngẫu nhiên}, NXB Đại học Quốc gia Hà Nội, 44-47.

\bibitem{pelletier_on_the_almost} Pelletier, M. (1998). {\em On The Almost Sure Asymtotic Behavior of Stochastic algorithms}.

\bibitem{pelletier_weak_convergence} Pelletier, M. (1998).{\em Weak convergence rates for stochastic approximation with application to multiple targets and simulated annealing}. Annals of Appli. Proba. 8, 1, 10-44.

\bibitem{nguyen_thanh_nhan} Trần Minh Phương, Nguyễn Thành Nhân (2022), {\em Giải tích số và ứng dụng (phần cơ bản)}, NXB Đại học Sư phạm TPHCM.

\bibitem{noda} Noda, K. (2007). Estimation of a Regression Function by The Parzen kernel-type Density Estimatiors, Ann Inst Statist Math, 221-234.

\bibitem{schuster} Schuster, E.F. (1972). Joint Asymptotic Distribution of The Esimated Regression Function at a Finite Number of distinct Points, 84-88.

\end{thebibliography}
